Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework

### 2018-03-21 paper.tex
Remove Appendix figures.

%FIGURE A1%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/n2-1000km.png}}
\appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa. Orange lines represent the cold-point tropopause height averaged over the same time periods.}
\label{fig:n2-1000km}
\end{figure*}

%FIGURE A2%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/turb-50m.png}}
\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab. Orange lines represent the cold-point tropopause height averaged over the same time periods.}
\label{fig:turb-50m}
\end{figure*}

>>>>

%%FIGURE A1%
%\begin{figure*}[ht]
%\centerline{\includegraphics[width=39pc]{figures/n2-1000km.png}}
%\appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa. Orange lines represent the cold-point tropopause height averaged over the same time periods.}
%\label{fig:n2-1000km}
%\end{figure*}
%
%%FIGURE A2%
%\begin{figure*}[ht]
%\centerline{\includegraphics[width=39pc]{figures/turb-50m.png}}
%\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab. Orange lines represent the cold-point tropopause height averaged over the same time periods.}
%\label{fig:turb-50m}
%\end{figure*}
